Sardines only end-to-end atlantisom test

### 2019-06-06 SardinesOnlyatlantisom2SStest.Rmd
progress? catch closer to correct

```{r true-catage-lf-wtage, eval=FALSE}

@@

Do true catch numbers times weight at age match catch in biomass? No. It is about 16 times too high relative to catch.txt output, and shifted one year back (which is due to the floor function, and an easy fix).

@@

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio from txt"),
            alpha = 10/10) +
  geom_point(data=catchbioN_ss, aes(x=yr,y=anncatchB/16, color="true catch bio from N/16"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

>>>>

```{r true-catage-lf-wtage}

@@

Do true catch numbers times weight at age match catch in biomass? It was about 16 times too high relative to catch.txt output, and shifted one year back (which is due to the floor function, and an easy fix).

June 6: just corrected the catch nums correction in `run_truth` and I hope it matches now.

@@

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio from txt"),
            alpha = 10/10) +
  geom_point(data=catchbioN_ss, aes(x=yr,y=anncatchB, color="true catch bio from N"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)
